Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-09 acl.2016/acl2016.tex
fucking rewrite

This paper not only focuses faster single-threaded decoding but also on overcoming the shortcomings of existing decoding implementations on multicore servers.

@@

For any phrase-table table of a realistic size, memory and loading time constraints requires us to use a load-on-demand implementation. Moses has several which we can make use of, each with differing performance characteristics. Figure~\ref{fig:moses-phrase-tables-time} shows the time taken to decode 800,000 sentences for the fastest two implementations.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{moses-phrase-table.png}} 
\end{tabular}
\caption{Moses decoding time with two different phrase-table implementations}
\label{fig:moses-phrase-tables-time}
\end{figure} 
From this, it appears that the Probing phrase-table~\cite{Bogoychev:Thesis:2013} has the fastest translation rule lookup, especially with large number of cores, therefore, we will concentrate exclusively on this implementation from hereon.

>>>>

This paper not only focuses on faster single-threaded decoding but also on overcoming the shortcomings of existing decoding implementations on multicore servers.

@@

For any phrase-table table of a realistic size, memory and loading time constraints requires us to use a load-on-demand implementation. Moses has several which we can make use of, each with differing performance characteristics. Figure~\ref{fig:moses-phrase-tables-time} shows the time taken to decode 800,000 sentences for the fastest two implementations.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{moses-phrase-table.png}} 
\end{tabular}
\caption{Moses decoding time with two different phrase-table implementations}
\label{fig:moses-phrase-tables-time}
\end{figure} 
From this, it appears that the Probing phrase-table~\cite{Bogoychev.probing.2016} has the fastest translation rule lookup, especially with large number of cores, therefore, we will concentrate exclusively on this implementation from hereon.
